Legends for supplementary material

### 2019-05-08 Manuscript/Supplementary/supplementary_legends.Rmd
consolidated supp fig and table into one table

**Supplementary Figure 14. Number of TADs called throughout the genome.** TADs were called throughout each of the 22 autosomal chromosomes for cell lines GM12878 (red) and K562 (blue) using the Arrowhead algorithm [@durand2016juicebox], across each data resolution including 10 kb, 25 kb, 50 kb, and 100 kb (A-D) respectively.

**Supplementary Table 8. Summary statistics for TAD lengths.** The following summary statistics were recorded regarding lengths of TADs that were called and delineated into TAD boundaries including the minimum, 1st quartile, median, mean, 3rd quartile, and maximum TAD lengths (in basepairs). The summaries are provided for each cell line, resolution, and within each chromosome. [???should I leave space for 9th chromosome on k562 where no TADs were called?]

>>>>

**Supplementary Table 8. Summary statistics for called TADs.** The following summary statistics were recorded regarding the average number and length of TADs (along with standard deviations) that were called using the Arrowhead algorithm [@durand2016juicebox], across each of the autosomal chromosomes (excluding chromosome 9).
